\documentclass[]{article}


\begin{document}

\section*{Manifesto for Agile Software Development\footnote{http://www.agilemanifesto.org/}}

We are uncovering better ways of developing
software by doing it and helping others do it.
Through this work we have come to value:

Individuals and interactions over processes and tools
Working software over comprehensive documentation
Customer collaboration over contract negotiation
Responding to change over following a plan

That is, while there is value in the items on
the right, we value the items on the left more.

\vspace{5mm}

\subsection*{Principles}

\begin{itemize}
	\item Our highest priority is to satisfy the customer through early and continuous delivery of valuable software.
	\item Welcome changing requirements, even late in development. Agile processes harness change for the customer's competitive advantage.
	\item Deliver working software frequently, from a couple of weeks to a couple of months, with a preference to the shorter timescale.
	\item Business people and developers must work together daily throughout the project.
	\item Build projects around motivated individuals. Give them the environment and support they need, and trust them to get the job done.
	\item The most efficient and effective method of conveying information to and within a development team is face-to-face conversation.
	\item Working software is the primary measure of progress.
	\item Agile processes promote sustainable development. The sponsors, developers, and users should be able to maintain a constant pace indefinitely.
	\item Continuous attention to technical excellence and good design enhances agility.
	\item Simplicity--the art of maximizing the amount of work not done--is essential.
	\item The best architectures, requirements, and designs emerge from self-organizing teams.
	\item At regular intervals, the team reflects on how to become more effective, then tunes and adjusts its behavior accordingly.
	
\end{itemize}



\end{document}
