\documentclass{article}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage[margin = 2.25cm]{geometry}




\begin{document}



\title{Day One Questionnaire\\IN700001 Capstone Project \\Semester One, 2016}
\date{}
\maketitle

\section*{Introduction}
We expect to put a large amount of time and effort into our projects throughout this year. Before we begin, we're going to spend a few minutes thinking about and making note of where we are starting from.  Please answer the questions below. We are going to use this information to make some plans for projects, and we will save these documents to consider when we prepare portfolios at the end of the year.

\section*{Name:}

\vspace{5mm}

\section*{Goals and strengths}

\begin{enumerate}
	\item What are you hoping to get out of project this year?
	\vspace{25mm}
	
	\item What do you hope to be doing in the first two years after you graduate?
	\vspace{25mm}
	
	\item What is the biggest strength that you bring to project?
	\vspace{25mm}
	
	\item List three or more of your most valued strengths \emph{of any kind}, not necessarily related to IT.
	\vspace{25mm}
	
	\item What is one area where you want to improve yourself this year?
	\vspace{25mm}
	
	
\end{enumerate}

\section*{Abilities and interests}
In this section you are asked to rate your ability and interest in a number of IT skill areas. You'll assign each a rating from 1 to 5, with 5 being the highest level.

Rate your \textbf{abilities}, relative to a ``typical'' BIT student at the start of the third year according to the following scale:

\begin{enumerate}
	\item My lack of ability is a problem I need to address this year.
	\item I am a little below average, but not alarmingly so.
	\item My ability level is about what you would expect from a student at the start of year 3.
	\item I have worked on this and ability is above average.
	\item My ability is stronger that expected for a BIT \emph{graduate}.
\end{enumerate}

Rate your \textbf{interest} according to this scale:

\begin{enumerate}
	\item I don't want to do any more than I must to pass.
	\item It's not my thing, but if I need to do some I'm OK with it.
	\item I'm happy to do it, but I'm equally happy if I don't.
	\item I really want to do some of this in project.
	\item I will be dissatisfied with project if I don't get to do this.
\end{enumerate}

\textbf{Programming} \qquad Ability: \qquad Interest: 
\vspace{5mm}

\textbf{Systems Admin} \qquad Ability: \qquad Interest: 
\vspace{5mm}

\textbf{Testing} \qquad Ability: \qquad Interest: 
\vspace{5mm}

\textbf{Documentation} \qquad Ability: \qquad Interest: 
\vspace{5mm}

\textbf{Web Development (front-end)} \qquad Ability: \qquad Interest: 
\vspace{5mm}

\textbf{Web Development (back-end)} \qquad Ability: \qquad Interest:
\vspace{5mm}

\textbf{Mobile Development} \qquad Ability: \qquad Interest:
\vspace{5mm}

\textbf{Hardware} \qquad Ability: \qquad Interest:
\vspace{5mm}

\textbf{Networking} \qquad Ability: \qquad Interest:
\vspace{5mm}

\textbf{Databases} \qquad Ability: \qquad Interest:
\vspace{5mm}

Did I miss anything?


\end{document}
